Exploring probability distributions for bivariate temporal granularities

### 2019-10-28 main.Rmd
rmd update with prob_plot

<!--temporal granularities and why should we care --> 
Temporal data can be available at various resolution depending on the context. Social and economic data are often collected and reported at coarser temporal scales like monthly, quarterly or annually. But with recent advancement in technology, more and more data are recorded and stored at much finer temporal scales than that was previously possible. It might be sufficient to observe energy consumption every half an hour, but energy supply needs to be monitored every minute and number of web searches requires optimization every second.  As the frequency of data increases, the number of questions about the observed variable that need to be addressed also increases. For example, data collected at an hourly scale can be analyzed using coarser temporal scales like days, months or quarters. This approach requires deconstructing time in various possible ways.

@@

# Formal conceptualization of calendar categorizations{#cirgran-def}

@@

## Linear time granularities{#linear-gran-def}

@@

The first condition implies that the granules in a linear granularity are non-overlapping and their index order is same as time order. \autoref{fig:linear-time} shows the implication of this condition. If we consider the bottom linear granularity [@aigner2011visualization] as hourly and the entire horizon has T hours then it will have $\lfloor T/24\rfloor$ days, $\lfloor s/(24*7)\rfloor$ weeks and so on.

@@

## Circular time granularities{#circular-gran-def}

A time domain, as defined by [@Bettini1998-ed], is essentially a mapping of row numbers (the index set) to the time index in a tsibble[@Wang2019-aw] for a given key. A linear granularity is a mapping of row numbers to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years. What we need to add to this are additional categorizations of time that are not linear granularities and are useful to represent periodicity.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
MOH: & $C_1(s)$ & $= s \mod 60$ & $n_1 =$&$60$ \\
MOD: & $C_2(s)$ & $= s \mod `r 60*24`$ & $n_2=$&$`r 60*24`$\\

HOD: & $C_4(s)$ & $= \lfloor s/60\rfloor\mod 24$  & $n_4 =$&$24$ \\
HOW: & $C_6(s)$ & $= \lfloor s/60\rfloor\mod 24*7$  & $n_5=$&$`r 24*7`$\\

DOW: & $C_7(s)$ & $= \lfloor s/24*60\rfloor \mod 7$ & $n_6=$&$7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative circular granularities with time index in minutes}
\label{definitions}
\end{table}

@@

We want to use modular arithmetic to define circular granularity. Hence, we start with the definition of equivalence classes and then move on to define a circular granularity.

<!-- Formal definition of circular granularity -->
**Definition: Equivalence class** Let $m \in N \backslash{0}$. For any $a \in Z$ (set of integers), $[a]$ is defined as the equivalence class to which a belongs if $[a]$ = {$b \in Z | a \equiv (b \mod m)$}.

@@

For example, suppose $C$ is a circular granularity denoting Hour-of-Day and we have hourly data for 100 hours. The modular period $m = 24$, since each day consists of 24 hours and $C$ is a mapping from ${1,2,\dots, 100}$ to ${0,1,2, \dots, 23}$ such that  $C(s)= s \mod 24$ for $s \in {1,2,\dots, 100}$.

@@

## Aperiodic time granularities{#aperiodic-gran-def}
<!-- Formal definition of aperiodic circular granularity -->

@@

# Single-order-up and multiple-order-up granularities

<!-- some discussions on primary units of calendar -->
So far we have used the Gregorian calendar as it is the most widely used calendar. But it is far from being the only one. All calendars fall under three types - solar, lunar or lunisolar/solilunar but the day is the basic unit of time underlying all calendars. Various calendars, however, use different conventions to structure days into larger units: weeks, months, years and cycle of years. Any civil day is divided into 24 hours and each hour into 60 minutes and each minute into 60 seconds. There are exceptions where in London, for example, length of each "hour" varies from about 39 minutes in December to 83 minutes in June. The French revolutionary calendar divided each day into 10 "hours", each "hour" into 100 "minutes" and each "minute" into 100 "seconds". Nevertheless, for any calendar, the hierarchical structure of time creates a natural nested ordering which can produce **single-order-up** or **multiple-order-up** granularities. We shall use the notion of a hierarchy table to define them.

Consider a **hierarchy table** to be consisting of two columns:  
 - The first column represents the (temporal) units in ascending order of hierarchy.  
 - The second column represents the constant which relates subsequent (temporal) units.

@@

We refer to granularities which are nested within multiple levels as **multiple-order-up** granularities and those concering a single level as **single-order-up** granularities. "Mayan" calendar is used to illustrate this. In Mayan calendar, one day was referred to as 1 kin and the calendar was structured as follows:

@@

## Computation of single-order-up granularities

Suppose, z denotes the index of the tsibble, x,y are two units in the hierarchy table  with  $order(x) <  order(y)$. Let $f(x, y)$ denotes the accessor function for computing the single-order-up granularity x-of-y and $c(x, y)$ is a constant which relates x and y.

@@

### Aperiodic single-order-up granularities

Aperiodic single-order-up granularities refers to the granularities which are formed with units that does not repeat its values in regular intervals or periods. In Gregorian calendar, examples may include days of the month where each month may consists of 28, 29, 30 or 31 days. So there is no single number that can be used for converting days to months. We cannot compute the aperiodic single-order-up granularities using the index of the tsibble and modular arithmetic like in the periodic case.

## Computation of multiple order-up granularities

@@

### All single-order-up granularities are periodic

z is the index set of the tsibble and x, y are two linear granularities with  $order(x) <  order(y)$. Also, $f(x, y)$ denotes the accessor function for computing circular granularity x_y and $c(x, y)$ is a constant which relates x and y. It is easy to see that for $order(x+1) =  order(y)$, the function is same as the single-order-up granularities.

@@

### Mixed single-order-up granularities - circular or aperiodic

@@

@@

  b) There should not be any level of the factor plotted across x-axis which doesn't have values for all levels of factors plotted across facets.
<!-- ## Distributions conditional on bivariate granularities -->

@@

library(ggplot2)
sm_cust50 %>%
  granplot("month_year", "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99)
  ) +
  ggtitle("") 
```

@@

# Hourly usage across days of the week
sm_cust50 %>%
  granplot("day_week", 
           "hour_day",
           "general_supply_kwh", 
           plot_type = "quantile", 
          quantile_prob = c(0.25, 0.5, 0.75),
           response = "general_supply_kwh", overlay = FALSE) +
  ggtitle("")

@@

```{r hhd-dm}
# Across days of the week by months
# sm_cust50 %>%
#   granplot("month_year",
#     "day_week",
#     response = "general_supply_kwh", plot_type = "quantile", 
#           quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99)) + ggtitle("") +
#   ggtitle("Quantile plot across day-of-week by month-of-year")

@@

# sm_cust50 %>%
#   dynamic_create_gran("day_week") %>%
#   filter(day_week %in% c("Sat", "Sun")) %>%
#   granplot("day_week", "week_month",
#            response = "general_supply_kwh",
#            plot_type = "lv") + 
#   ggtitle("")

# 
# sm_cust50 %>%
#   granplot( "hhour_hour","hour_day",
#            response = "general_supply_kwh",
#            plot_type = "quantile", overlay = TRUE) + 
#   ggtitle("")

sm_cust50 %>%
  granplot( "hhour_day","day_month",
           response = "general_supply_kwh",
           plot_type = "quantile", overlay = TRUE) + 
  ggtitle("")
```

@@

```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons."}
  cricket_tsibble_all %>% 
  granplot("over", "season",
                                hierarchy_model,
                                response = "runs_per_over",
                                plot_type = "quantile",
                                quantile_prob = c(0.25, 0.5, 0.75), overlay = FALSE

@@

 MI_winner %>% 
            granplot( "win","inning",
                                hierarchy_model,
                                response = "run_rate",
                                plot_type = "violin",
                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
                     overlay = FALSE) + ggtitle("") + 
    geom_boxplot(width = 0.1, color = "blue")

 CSK_winner %>% filter(inning %in% c(1,2)) %>% 
           granplot( "win","inning",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
                    overlay = FALSE) + ggtitle("") + 
   geom_boxplot(width = 0.1, color = "blue")
```

@@

<!-- ```{r 2013_15_MI} -->
<!--  cricket_tsibble_all %>%  -->
<!--   filter(season %in% c(2013, 2015), batting_team=="Mumbai Indians") %>%  -->
<!--            granplot("inning", "over", -->
<!--                                hierarchy_model, -->
<!--                                response = "run_rate", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

<!--   )  + #scale_y_discrete(breaks= seq(1, 25,1)) + -->
<!--     theme( # remove the vertical grid lines -->
<!--            panel.grid.major.x = element_blank() , -->
<!--            # explicitly set the horizontal lines (or they will disappear too) -->
<!--            panel.grid.major.y = element_line( size=.1, color="white" )  -->
<!--     ) -->
<!--  cricket_tsibble_all %>%  -->
<!--   filter(season %in% c(2013, 2015), batting_team=="Chennai Super Kings") %>%  -->
<!--            granplot("inning", "over", -->
<!--                                hierarchy_model, -->
<!--                                response = "run_rate", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

CSK <- cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015),
         batting_team=="Chennai Super Kings",
         inning %in% c(1,2))

@@

MI %>% 
  granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

CSK %>% 
  granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")

@@

cricket_tsibble_fld %>% 
  filter(fielding_wckts %in% c(0,1,2)) %>% 
  granplot( "fielding_wckts","over",
                               hierarchy_model,
                               response = "lagged_run_rate",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("")

@@

```{r dot, fig.cap="Distribution of run rate across overs of the innings and number of dot balls in an over."}
cricket_dot <- cricket_season %>% 
  mutate(wicket = if_else(is.na(dismissal_kind),0,1),
         dot_balls = if_else(total_runs==0,1, 0)
         ) %>% 
  group_by(season, match_id, batting_team, bowling_team,  inning, over) %>%
  summarise(runs_per_over = sum(total_runs), run_rate = sum(total_runs)/length(total_runs),
            wicket = sum(wicket),
            dot_balls = sum(dot_balls))

@@

cricket_tsibble_dot  %>% filter(dot_balls %in% c(1,2,3,4)) %>% 
  granplot("over","dot_balls",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = FALSE)  + ggtitle("")
```

<!--   cricket_tsibble %>% granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + -->
<!--     theme( # remove the vertical grid lines -->
<!--            panel.grid.major.x = element_blank() , -->
<!--            # explicitly set the horizontal lines (or they will disappear too) -->
<!--            panel.grid.major.y = element_line( size=.1, color="black" )  -->
<!--     ) -->

<!--   cricket_tsibble %>% -->
<!--     filter(batting_team == "Chennai Super Kings") %>%  -->
<!--     granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

<!--     cricket_tsibble %>% -->
<!--     filter(batting_team == "Kolkata Knight Riders") %>%  -->
<!--     granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

@@

<!--   cricket_tsibble_all %>% granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble_all %>% granplot("inning_match", "season", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble_all %>% granplot("season", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble %>% -->
<!--     filter(batting_team == "Chennai Super Kings") %>%  -->
<!--     granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

<!--     cricket_tsibble %>% -->
<!--     filter(batting_team == "Kolkata Knight Riders") %>%  -->
<!--     granplot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

>>>>

<!--temporal granularities and why should we care --> 
Temporal data can be available at various resolution depending on the context. Social and economic data are often collected and reported at coarser temporal scales like monthly, quarterly or annually. But with recent advancement in technology, more and more data are recorded and stored at much finer temporal scales. Energy consumption is collected every half an hour, while energy supply is collected every minute and web search data might be collected at every second. As the frequency of data increases, the number of questions about the observed variable that need to be addressed also increases. For example, data collected at an hourly scale can be analyzed using coarser temporal scales like days, months or quarters. This approach requires deconstructing time in various possible ways.

@@

# Definitions of time granularities{#cirgran-def}

@@

## Linear {#linear-gran-def}

@@

The first condition implies that the granules in a linear granularity are non-overlapping and their index order is same as time order. \autoref{fig:linear-time} shows the implication of this condition. If we consider the bottom linear granularity [@aigner2011visualization] as hourly and the entire horizon has T hours then it will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.

@@

## Circular {#circular-gran-def}

Periodicity is very common in all kinds of data and circular granularities can be construed to reflect such periodicities. Circular granularities can be constructed by putting to use two linear granularities. However, mappings between linear granularities can be regular or irregular. For example, a regular mapping exists between minutes and hours, where 60 minutes always add up to 1 hour. On contrary, an irregular mapping exists between days and months, since one might can have days ranging from 28 to 31. Hence, circular granularities can also be "periodic" or "aperiodic" depending on

A linear granularity, as defined by [@Bettini1998-ed], is essentially a mapping of the index set to subsets of the bottom granularity. For example, if the bottom granularity is days, then a linear granularity might be weeks, months or years. Here, the domain is the index set and range is subsets of bottom granularity. Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of bottom granularity. They also accomodate periodicity and hence the smaller subsets of bottom granularity are nested within the larger subsets of bottom granularity. We use modular arithmetic to define circular granularity and use the following definitions:

<!-- What we need to add to this are additional categorizations of time that are not linear granularities and are useful to represent periodicity. -->

<!-- \begin{table}[ht] -->
<!-- \begin{center} -->
<!-- \begin{tabular}{lr@{~}lr@{~}r} -->
<!-- \toprule -->
<!-- MOH: & $C_1(s)$ & $= s \mod 60$ & $n_1 =$&$60$ \\ -->
<!-- MOD: & $C_2(s)$ & $= s \mod `r 60*24`$ & $n_2=$&$`r 60*24`$\\ -->

<!-- HOD: & $C_4(s)$ & $= \lfloor s/60\rfloor\mod 24$  & $n_4 =$&$24$ \\ -->
<!-- HOW: & $C_6(s)$ & $= \lfloor s/60\rfloor\mod 24*7$  & $n_5=$&$`r 24*7`$\\ -->

<!-- DOW: & $C_7(s)$ & $= \lfloor s/24*60\rfloor \mod 7$ & $n_6=$&$7$\\ -->
<!-- \bottomrule -->
<!-- \end{tabular} -->
<!-- \end{center} -->
<!-- \caption{Illustrative circular granularities with time index in minutes} -->
<!-- \label{definitions} -->
<!-- \end{table} -->

@@

<!-- Formal definition of circular granularity -->

**Definition: Equivalence class** Let $m \in N \backslash{0}$. For any $a \in Z$ (set of integers), $[a]$ is defined as the equivalence class to which a belongs if $[a]$ = {$b \in Z | a \equiv (b \mod m)$}.

@@

For example, suppose $C$ is a circular granularity denoting hour-of-day and we have hourly data for 100 hours. The modular period $m = 24$, since each day consists of 24 hours and $C$ is a mapping from ${1,2,\dots, 100}$ to ${0,1,2, \dots, 23}$ such that  $C(s)= s \mod 24$ for $s \in {1,2,\dots, 100}$.

@@

## Aperiodic {#aperiodic-gran-def}
<!-- Formal definition of aperiodic circular granularity -->

@@

# Computation of time granularities

## Definitions of time granularities based on order

The hierarchical structure of time creates a natural nested ordering which can produce **single-order-up** or **multiple-order-up** granularities. We shall use the notion of a hierarchy table to define them.

Consider a **hierarchy table** to be consisting of two columns:

 -  The first column represents the (temporal) units in ascending order of hierarchy. Any two units can join together to form a granularity.

 - The second column represents the relationship between subsequent (temporal) units. For periodic granularities, this could be represented by a constant, whereas, for a aperiodic one, there is no single constant which can be used to represent their relationship.

@@

We refer to granularities which are nested within multiple levels as **multiple-order-up** granularities and those concering a single level as **single-order-up** granularities. Let us look at few calendars to see examples of single and multiple order-up granularities.

<!-- some discussions on primary units of calendar -->
So far we have used the Gregorian calendar as it is the most widely used calendar. But it is far from being the only one. All calendars fall under three types - solar, lunar or lunisolar/solilunar but the day is the basic unit of time underlying all calendars. Various calendars, however, use different conventions to structure days into larger units: weeks, months, years and cycle of years. Any civil day is divided into 24 hours and each hour into 60 minutes and each minute into 60 seconds. There are exceptions where in London, for example, length of each "hour" varies from about 39 minutes in December to 83 minutes in June. The French revolutionary calendar divided each day into 10 "hours", each "hour" into 100 "minutes" and each "minute" into 100 "seconds". Nevertheless, for any calendar a hierarchy can be defined. For example, in Mayan calendar, one day was referred to as 1 kin and the calendar was structured as follows:

@@

### Single-order-up granularities

Suppose, z denotes the index of the tsibble, x,y are two units in the hierarchy table  with  $order(x) <  order(y)$. Let $f(x, y)$ denotes the accessor function for computing the single-order-up granularity relating x and y and $c(x, y)$ is a constant which relates x and y.

@@

#### Aperiodic single-order-up granularities

Aperiodic single-order-up granularities refers to the granularities which are formed with units that does not repeat its values in regular intervals or periods. In Gregorian calendar, examples may include days of the month where each month may consists of 28, 29, 30 or 31 days. So there is no single number that can be used for converting days to months. We cannot compute the aperiodic single-order-up granularities using the index of the tsibble and modular arithmetic like in the periodic case using just the hierarchy table and relationships of units.

### Computation of multiple order-up granularities

@@

#### All single-order-up granularities are periodic

z is the index set of the tsibble and x, y are two linear granularities with  $order(x) <  order(y)$. Also, $f(x, y)$ denotes the accessor function for computing circular granularity which relates x and y and $c(x, y)$ is a constant which relates x and y. It is easy to see that for $order(x+1) =  order(y)$, the function is same as the single-order-up granularities.

@@

#### Mixed single-order-up granularities - circular or aperiodic

@@

# Interaction

@@

  b) There should not be any level of the factor plotted across x-axis which doesn't have values for all levels of factors plotted across facets.

<!-- ## Distributions conditional on bivariate granularities -->

@@

library(ggplot2)
sm_cust50 %>%
  prob_plot("month_year", "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99)
  ) +
  ggtitle("") 
```

@@

# Hourly usage across days of the week
sm_cust50 %>%
  prob_plot("day_week", 
           "hour_day",
           "general_supply_kwh", 
           plot_type = "quantile", 
          quantile_prob = c(0.25, 0.5, 0.75),
           response = "general_supply_kwh", overlay = FALSE) +
  ggtitle("")

@@

```{r hhd-dm}
# Across days of the week by months
# sm_cust50 %>%
#   prob_plot("month_year",
#     "day_week",
#     response = "general_supply_kwh", plot_type = "quantile", 
#           quantile_prob = c(0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95, 0.99)) + ggtitle("") +
#   ggtitle("Quantile plot across day-of-week by month-of-year")

@@

# sm_cust50 %>%
#   dynamic_create_gran("day_week") %>%
#   filter(day_week %in% c("Sat", "Sun")) %>%
#   prob_plot("day_week", "week_month",
#            response = "general_supply_kwh",
#            plot_type = "lv") + 
#   ggtitle("")

# 
# sm_cust50 %>%
#   prob_plot( "hhour_hour","hour_day",
#            response = "general_supply_kwh",
#            plot_type = "quantile", overlay = TRUE) + 
#   ggtitle("")

sm_cust50 %>%
  prob_plot( "hhour_day","day_month",
           response = "general_supply_kwh",
           plot_type = "quantile", overlay = TRUE) + 
  ggtitle("")
```

@@

```{r seas-over-inning, fig.cap = "Quantile plot of runs per over across overs of different seasons."}
  cricket_tsibble_all %>% 
  prob_plot("over", "season",
                                hierarchy_model,
                                response = "runs_per_over",
                                plot_type = "quantile",
                                quantile_prob = c(0.25, 0.5, 0.75), overlay = FALSE

@@

 MI_winner %>% 
            prob_plot( "win","inning",
                                hierarchy_model,
                                response = "run_rate",
                                plot_type = "violin",
                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
                     overlay = FALSE) + ggtitle("") + 
    geom_boxplot(width = 0.1, color = "blue")

 CSK_winner %>% filter(inning %in% c(1,2)) %>% 
           prob_plot( "win","inning",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
                    overlay = FALSE) + ggtitle("") + 
   geom_boxplot(width = 0.1, color = "blue")
```

@@

<!-- ```{r 2013_15_MI} -->
<!--  cricket_tsibble_all %>%  -->
<!--   filter(season %in% c(2013, 2015), batting_team=="Mumbai Indians") %>%  -->
<!--            prob_plot("inning", "over", -->
<!--                                hierarchy_model, -->
<!--                                response = "run_rate", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

<!--   )  + #scale_y_discrete(breaks= seq(1, 25,1)) + -->
<!--     theme( # remove the vertical grid lines -->
<!--            panel.grid.major.x = element_blank() , -->
<!--            # explicitly set the horizontal lines (or they will disappear too) -->
<!--            panel.grid.major.y = element_line( size=.1, color="white" )  -->
<!--     ) -->
<!--  cricket_tsibble_all %>%  -->
<!--   filter(season %in% c(2013, 2015), batting_team=="Chennai Super Kings") %>%  -->
<!--            prob_plot("inning", "over", -->
<!--                                hierarchy_model, -->
<!--                                response = "run_rate", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

CSK <- cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015),
         batting_team=="Kolkata Knight Riders",
         inning %in% c(1,2))

@@

MI %>% 
  prob_plot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

CSK %>% 
  prob_plot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")

cricket_tsibble_all %>% distinct(batting_team)

@@

cricket_tsibble_fld %>% 
  filter(fielding_wckts %in% c(0,1,2)) %>% 
  prob_plot( "fielding_wckts","over",
                               hierarchy_model,
                               response = "lagged_run_rate",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("")

@@

```{r dot, fig.cap="Distribution of run rate across overs of the innings and number of dot balls in an over."}

cricket_dot <- cricket_season %>% 
  mutate(wicket = if_else(is.na(dismissal_kind),0,1),
         dot_balls = if_else(total_runs==0,1, 0)
         ) %>% 
  group_by(season, match_id, batting_team, bowling_team,  inning, over) %>%
  summarise(runs_per_over = sum(total_runs), run_rate = sum(total_runs)/length(total_runs),
            wicket = sum(wicket),
            dot_balls = sum(dot_balls))

@@

cricket_tsibble_dot  %>% filter(dot_balls %in% c(1,2,3,4)) %>% 
  prob_plot("over","dot_balls",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = FALSE)  + ggtitle("")
```

<!--   cricket_tsibble %>% prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + -->
<!--     theme( # remove the vertical grid lines -->
<!--            panel.grid.major.x = element_blank() , -->
<!--            # explicitly set the horizontal lines (or they will disappear too) -->
<!--            panel.grid.major.y = element_line( size=.1, color="black" )  -->
<!--     ) -->

<!--   cricket_tsibble %>% -->
<!--     filter(batting_team == "Chennai Super Kings") %>%  -->
<!--     prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

<!--     cricket_tsibble %>% -->
<!--     filter(batting_team == "Kolkata Knight Riders") %>%  -->
<!--     prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

@@

<!--   cricket_tsibble_all %>% prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble_all %>% prob_plot("inning_match", "season", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble_all %>% prob_plot("season", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->

@@

<!--   cricket_tsibble %>% -->
<!--     filter(batting_team == "Chennai Super Kings") %>%  -->
<!--     prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->

<!--     cricket_tsibble %>% -->
<!--     filter(batting_team == "Kolkata Knight Riders") %>%  -->
<!--     prob_plot("inning_match", "over_inning", -->
<!--                                hierarchy_model, -->
<!--                                response = "runs_per_over", -->
<!--                                plot_type = "quantile", -->
<!--                                quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9) -->
<!--   ) -->
